Capstone Movielens Report

### 2025-12-10 reports/capstone-movielens.site/05.appendix.Rmd
Minor fix for function description: loess_de.

The source code of the [loess_de](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L71) function is shown below:
```{r eval=FALSE}
loess_de <- function(de_bias.dat, degree = NA, span = NA){
  if(is.na(degree)) degree = 1
  if(is.na(span)) span = 0.75
  loess(de ~ days, span = span, degree = degree, data = de_bias.dat)
}
```

>>>>

The source code of the [loess_de](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L71) function is shown below:
```{r eval=FALSE}
loess_de <- function(de_bias.dat, degree = NA, span = NA){
  if(is.na(degree)) degree = 1
  if(is.na(span)) span = 0.75
  loess(de ~ days, span = span, degree = degree, data = de_bias.dat)
}
```
